Meta-analysis of fungicide application timing experiments for powdery mildew management

### 2020-04-02 03_Prep_data.Rmd
Updated filepaths

write.csv(PM_MB_means,
          "data/1911_PM_MB_means&Ygains.csv")
```

@@

write.csv(slimmer_PM_dat, file = "data/slimmer_PM_clusterdat.csv", row.names = FALSE)
```

>>>>

write.csv(PM_MB_means,
          "cache/1911_PM_MB_means&Ygains.csv")
```

@@

write.csv(slimmer_PM_dat, file = "cache/slimmer_PM_clusterdat.csv", row.names = FALSE)
```
